Kyoto VR MQP Paper First Draft

### 2019-09-21 paper.tex
add to testing section

With the ground-plane detection features stripped away from the main app, the
AR focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
Atticus took photographs of various signs throughout Kinkakuji for us to use as
image targets. Hikaru Inoue helped us by translating all of the text in these
photos from Japanese to English. In this design, the AR camera superimposes an
``info'' button on top of the sign. Tapping on this button brings up a separate
UI element containing the translation, which can be seen in
Figure~\ref{fig:signTranslation}.

@@

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
	\caption[The original version of the Kinkakuji tour]{The original version of
    the Kinkakuji tour with small regions}
	\label{fig:kinkakujiTour}
\end{figure}

Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji} to
create a second, ``chunkier'' tour.  In the tour-file \texttt{kinkakuji-chunkier},
we expanded all of the regions to accomodate for potential GPS inaccuracies
that could place the user outside the range of the audio-trigger region.
Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour that we used for field
testing at Kinkakuji.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
	\caption[The ``chunkier'' version of the Kinkakuji tour]{The ``chunkier'' version of
    the Kinkakuji tour with larger regions}
	\label{fig:kinkakujiChunkierTour}
\end{figure}

@@

Our previous testing involved creating a ``mock tour'' on the Ritsumeikan campus.
While this let us know generally which features of the app were working, it was
very difficult to know how ahead of time how well our app would work at Kinkakuji.

We were surprised by how intuitively each region triggered on the first try.
With a few exceptions, the audio started when the subject of the audio track
was in view. During our first walkthrough of Kinkakuji, we triggered every
region and audio track but one. The region that we missed on the first pass,
``Final Viewpoint'', requires the user to take a right at a fork in the road
instead of continuing along the main path. This is not necessarily a problem
with the design of the regions; instruction provided by the audio tour could
remedy this, directing the user toward the viewpoint that is off of the main
path.

@@

Other bugs resulted from oversights that were difficult to catch with our
on-campus testing.  For example, we noticed that we forgot to back-up the audio
slider when entering a new region.  Because of this, when we entered a new
region when the audio slider was past the endpoint of the new audio track, the
audio would not play. For example, if the previous audio track were a minute
long, and if the second track were only thirty seconds long, the app would try
to play a thirty second audio track from the one minute mark. Since we were
running the app on phones, we could not easily see when errors were thrown.
Similarly, if the user were to enter a new region while thirty seconds into the
previous audio track, the new audio track would start at the thirty second
mark. During our on-campus testing, we were using songs rather than narration.
Since the songs were relatively long and not always obvious when they started
partway through, we did not catch this until we got out to Kinkakuji. Luckily,
this was trivial to fix.

>>>>

With the ground-plane detection features stripped away from the main app, the
AR focus shifted to translating the maps and signs using the camera. The fourth
screen on Figure~\ref{fig:adobeXdDesign} shows a mock-up of this feature.
Atticus took photographs of various signs throughout Kinkaku-ji for us to use as
image targets. Hikaru Inoue helped us by translating all of the text in these
photos from Japanese to English. In this design, the AR camera superimposes an
``info'' button on top of the sign. Tapping on this button brings up a separate
UI element containing the translation, which can be seen in
Figure~\ref{fig:signTranslation}.

@@

Both pieces of our project---the Editour and ARuko---are designed to be used by
people who aren't programmers. The Editour will be used by Atticus in the future
to design more tours, and ARuko will be used by the general public. Because of
this, we needed to do extensive testing to ensure not only that the products
work as intended without bugs, but also that they would be pleasant and easy to
use for their intended users.

\subsection{Testing Editour}
\label{sec:testingEditour}

\subsection{Testing ARuko}
\label{sec:aruko}

\subsubsection{First Round of Field Testing}
\label{sec:firstRoundOfFieldTesting}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-tour.png}
	\caption[The original version of the Kinkaku-ji tour]{The original version
		of the Kinkaku-ji tour with small regions}
	\label{fig:kinkakujiTour}
\end{figure}

Due to concerns about GPS accuracy, we adapted the tour-file \texttt{kinkakuji}
to create a second, ``chunkier'' tour.  In the tour-file
\texttt{kinkakuji-chunkier}, we expanded all of the regions to accomodate for
potential GPS inaccuracies that could place the user outside the range of the
audio-trigger region.  Figure~\ref{fig:kinkakujiChunkierTour} depicts the tour
that we used for field testing at Kinkaku-ji.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{kinkakuji-chunkier-tour.png}
	\caption[The ``chunkier'' version of the Kinkaku-ji tour]{The ``chunkier''
		version of the Kinkaku-ji tour with larger regions}
	\label{fig:kinkakujiChunkierTour}
\end{figure}

@@

Our previous testing involved creating a ``mock tour'' on the Ritsumeikan
campus. While this let us know generally which features of the app were working,
it was very difficult to know how ahead of time how well our app would work at
Kinkaku-ji.

We were surprised by how intuitively each region triggered on the first try.
With a few exceptions, the audio started when the subject of the audio track
was in view. During our first walkthrough of Kinkaku-ji, we triggered every
region and audio track but one. The region that we missed on the first pass,
``Final Viewpoint'', requires the user to take a right at a fork in the road
instead of continuing along the main path. This is not necessarily a problem
with the design of the regions; instruction provided by the audio tour could
remedy this, directing the user toward the viewpoint that is off of the main
path.

@@

Other bugs resulted from oversights that were difficult to catch with our
on-campus testing.  For example, we noticed that we forgot to back-up the audio
slider when entering a new region.  Because of this, when we entered a new
region when the audio slider was past the endpoint of the new audio track, the
audio would not play. For example, if the previous audio track were a minute
long, and if the second track were only thirty seconds long, the app would try
to play a thirty second audio track from the one minute mark. Since we were
running the app on phones, we could not easily see when errors were thrown.
Similarly, if the user were to enter a new region while thirty seconds into the
previous audio track, the new audio track would start at the thirty second
mark. During our on-campus testing, we were using songs rather than narration.
Since the songs were relatively long and not always obvious when they started
partway through, we did not catch this until we got out to Kinkaku-ji. Luckily,
this was trivial to fix.
